FoRTE baseline

### 2019-10-25 analysis/paper/paper.Rmd
Fix LaTeX table formatting

```{r setup, include = FALSE}
library(knitr)
library(here)

@@

| Name                         | Description                                                                          | Color                     |
|------------------------------|--------------------------------------------------------------------------------------|---------------------------|
| **Crown model**              |                                                                                      |                           |
| `closed` (default)           | Cohort crowns take up entire patch area. Competition for light based only on height. | Light                     |
| `finite`                     | Cohort crown area is proportional to DBH according to PFT-specific allometry.        | Dark                      |
| **Radiative transfer model** |                                                                                      |                           |
| `two-stream` (default)       | Two-stream approximation [@sellers_1985_canopy; @clm45_note]                         | Primary (red, blue)       |
| `multi-scatter`              | Multiple-scatter approximation, following [@zhao_2005_multiple]                      | Secondary (green, orange) |
| **Trait plasticity**         |                                                                                      |                           |
| `static` (default)           | SLA and V~c,max~ are constant                                                        | Cool (blue, green)        |
| `plastic`                    | SLA increases, and V~c,max~ decreases, with light level                              | Warm (red, orange)        |

@@

The full list of parameters in ED-2.2 is large, with over 100 parameters per plant functional type.
A full sensitivity and uncertainty analysis across all of these parameters is outside the scope of this study.
Instead, we selected a subset of parameters guided by (but expanding upon) previous ED2 sensitivity studies [@dietze_2014_quantitative; @raczka_2018_what; @viskari_2019_influence].

@@

```{r param-table}
tbl <- readr::read_csv(here(
  "analysis", "data", "derived-data", "parameter-table.csv"
))
tbl <- subset(tbl, Ran == "yes", select = c(-unit_parsed, -Ran))
tbl[["ED Name"]] <- sprintf("`%s`", tbl[["ED Name"]])
kable(tbl, escape = FALSE, caption = paste0(
  "Table 2: Parameter descriptions. ",
  "For additional information, see the ",
  "[ED2 model wiki](https://github.com/EDmodel/ED2/wiki/PFT-parameters)."
))
```

>>>>

```{r setup, include = FALSE}
library(knitr)
library(here)
library(magrittr)
library(kableExtra)

@@

| Name | Description | Color |
|------|-------------|-------|
| **Crown model** |||
| **C**losed (default) | Cohort crowns take up entire patch area. Competition for light based only on height. | Light |
| **F**inite | Cohort crown area is proportional to DBH according to PFT-specific allometry. | Dark |
| **Radiative transfer model** |||
| **T**wo-stream (default) | Two-stream approximation [@sellers_1985_canopy; @clm45_note] | Primary (red, blue) |
| **M**ulti-scatter | Multiple-scatter approximation, following [@zhao_2005_multiple] | Secondary (green, orange) |
| **Trait plasticity** |||
| **S**tatic (default) | SLA and V~c,max~ are constant | Cool (blue, green) |
| **P**lastic | SLA increases, and V~c,max~ decreases, with light level | Warm (red, orange) |

@@

The full list of parameters in ED-2.2 is large, with over 100 parameters per plant functional type.
A full sensitivity and uncertainty analysis across all of these parameters is outside the scope of this study.
Instead, we selected a subset of parameters guided by (but expanding upon) previous ED-2.2 sensitivity studies [@dietze_2014_quantitative; @raczka_2018_what; @viskari_2019_influence].

@@

```{r param-table}
tbl <- readr::read_csv(here(
  "analysis", "data", "derived-data", "parameter-table.csv"
))
tbl <- subset(tbl, Ran == "yes", select = c(-unit_parsed, -Ran))
tbl[["ED Name"]] <- sprintf("`%s`", tbl[["ED Name"]])
kable(tbl, escape = is_latex_output(), caption = paste0(
  "Table 2: Parameter descriptions. ",
  "For additional information, see the ",
  "[ED2 model wiki](https://github.com/EDmodel/ED2/wiki/PFT-parameters)."
), booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```
